What paradigms can webcam eye-tracking be used for? Attempted replications of five ``classic'' cognitive science experiments

### 2025-03-30 manuscript.Rmd
Saved visual changes from R studio

---
title             : "What paradigms can webcam eye-tracking be used for? Attempted replications of five prominent cognitive science experiments"
shorttitle        : "Webcam eye-tracking paradigms"

author:
  - name: Ariel N. James
    affiliation: '1'
    role:
      - Conceptualization
      - Formal analysis
      - Visualization
      - Writing - original draft
      - Writing - review & editing
    email: ajames2@macalester.edu
    corresponding: yes
    address: 1600 Grand Ave, Saint Paul, MN 550105, USA

@@

    email: joshua.hartshorne@bc.edu

@@

affiliation:
  - id: '1'
    institution: Psychology Department, Macalester College
  - id: '2'
    institution: Department of Cognitive & Information Science, University of California,
      Merced
  - id: '3'
    institution: Department of Communication Sciences and Disorders, MGH Institute of Health Professions
  - id: '4'
    institution: Cognitive Science Department, Vassar College

abstract: |
  Web-based data collection allows researchers to recruit large and diverse samples with fewer resources than lab-based studies require. Recent innovations have expanded the set of methodolgies that are possible online, but ongoing work is needed to test the suitability of web-based tools for various research paradigms. Here, we focus on webcam-based eye-tracking; we tested whether the results of five different eye-tracking experiments in the cognitive psychology literature would replicate in a webcam-based format. Specifically, we carried out five experiments by integrating two javascript-based tools: jsPsych and a modified version of Webgazer.js. In order to represent a wide range of applications of eye-tracking to cognitive psychology, we chose two psycholinguistic experiments, two memory experiments, and a decision-making experiment. These studies also varied in the type of eye-tracking display, including screens split into halves (Exps. 3 and 5) or quadrants (Exps. 2 and 4), or composed scenes with regions of interest that varied in size (Exp. 1). Outcomes were mixed. The least successful replication attempt was Exp. 1; we did not obtain a condition effect in our remote sample (1a), nor in an in-lab follow-up (1b). However, the other four experiments were more successful, replicating a blank-screen effect (Exp. 2), a novelty preference (Exp. 3), a verb bias effect (Exp. 4), and a gaze-bias effect in decision-making (Exp. 5). These results suggest that webcam-based eye tracking can be used to detect a variety of cognitive phenomena, including those with sensitive time, although paradigms that require high spatial resolution (like Exp. 1) should be adapted to coarser quadrant or split-half displays.

keywords          : "eye-tracking, online, webcam, jsPsych, cognitive science"
wordcount         : "X"

bibliography      : ["references.bib"]

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

@@

The use of eye-tracking to study cognition took off when Alfred Yarbus used suction cups to affix a mirror system to the sclera of the eye in order to monitor eye position during the perception of images [@yarbus1967eye]. In one study, participants viewed a painting depicting multiple people in a complex interaction inside of a 19th century Russian home. Yarbus showed, among other things, that the scan paths and locations of fixations were largely dependent on the instructions given to participants (e.g., View the picture freely vs. Remember the position of the people and objects in the room). In other words, the cognitive processing that the individual is engaged in drives the visuo-motor system. Since these findings, eye-tracking has become a central method in cognitive science research [for reviews see @hayhoe2005eye; @richardsonEyeTrackingResearch2004; @rayner1998eye]. For example, gaze location during natural scene perception is used to test theories of visual attention [e.g., @henderson2017meaning], and eye-movements during auditory language comprehension, using the "visual world paradigm," demonstrated the context-dependent and incremental nature of language processing [e.g., @tanenhaus1995].

An important limitation of the eye-tracking methodology is that it has typically required costly equipment (eye-trackers can range in price from a few thousand dollars to tens of thousands of dollars), particular laboratory conditions (a quiet room with consistent indoor lighting conditions), and a substantial time investment (e.g., bringing participants into a laboratory one at a time). This limits who can conduct eye-tracking research -- not all researchers have the necessary resources -- and who can participate in eye-tracking research. Most eye-tracking study participants are from western, educated, industrialized, rich, and democratic [WEIRD, @henrich2010weirdest] convenience samples [but see @ryskin2023real], which diminishes the generalizability of the findings and the scope of conclusions that can be drawn about human cognition. Likewise, the sample sizes for in-lab experiments are usually orders of magnitude smaller than what statisticians recommend [@nosek2022replicability].

A robust solution to all these problems is online experiments, particularly with volunteer citizen scientists as participants [@li2024developmental; @hartshorne2019thousand; @reinecke2015labinthewild; @gosling2010wired]. Historically, this option has not been available for eye-tracking, since few potential subjects have expensive eyetrackers at home. In principal, this could be circumvented by using so-called "poor-man's" eye-tracking, in which researchers videotape the subject's face and code eye position frame-by-frame [@snedeker2003using]. Most computers now have high-quality built-in cameras, so recording video is straightforward. Unfortunately, coding images frame-by-frame is extremely time-intensive, making large-sample studies unrealistic. However, in recent years, image analysis has improved to the point where this work can be automated with reasonable accuracy [@papoutsaki2016webgazer; @zheng2018rapid; @burton2014comparison; @skovsgaard2011evaluation]. Nonetheless, webcam-based eyetracking only started to be used regularly in research with the advent of `Webgazer.js` [@papoutsaki2016webgazer], a webcam-based Javascript plug-in that works in the browser and which can be integrated with any Javascript web interface, including `jsPsych` [@deleeuwJsPsychJavaScriptLibrary2015], `Gorilla` [@anwyl2020gorilla], `lab.js` [@henninger2021lab], or `PsychoJS` [@peirce2019psychopy2].

@@

While promising, there are some salient limitations. First, many of the studies report effects that are smaller or later than what had been previously observed in the lab [@slim2024webcams; @van2024validation; @slim2022moving; @degen2021seeing; @van2023validation; @bogdan2024investigating; @kandel2024assessing]. Some of this is likely due to programming errors rather than inherent limitations in the technology: Importantly, accurate timing on a web browser is not trivial [@passell2021cognitive; @de2016psychophysics], and subtle programming choices can significantly affect the accuracy of `WebGazer.js` timing [@yang2021webcam].[^1] Since most of the prior work did not address these timing issues, it is not clear how many of the reported lab/web differences would resolve.

@@

Second, prior work has focused on studies with relatively coarse-grained regions of interest [but see @semmelmann2018online; @bogdan2024investigating], dividing the screen either in half or in quadrants. This is particularly salient with [@prystauka2023online], which simplified @altmannIncrementalInterpretationVerbs1999's design so that regions of interest are quadrants rather than the finer-grained ROIs used in the original. Certainly, webcam eyetracking will not be as spatially fine-grained as an infrared eyetracker, but we do not yet have a good sense of the limits.

@@

In order to broaden the validation of online eye-tracking methodology, we set out to reproduce five previously published studies representing a variety of questions, topics, and paradigms. The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science, across a broad range of research areas. Critically, we used the only implementation known to have addressed a critical bug in the timing precision of WebGazer.js, specifically the one in `jsPsych`, a package which is known in general for having particularly good timing precision [@de2016psychophysics; @bridges2020timing].

@@

We chose five high-impact eye-tracking studies involving adult subjects [for a comparison of remote WebGazer and in-lab anticipatory looking effects with 18-27 month-old participants, see @steffan2024validation]. Our goal was to include experiments from a range of topic areas (e.g., memory, decision making, psycholinguistics) and paradigms (two halves of the screen, visual world paradigm with four quadrants, visual world paradigm with "naturalistic" scenes). As noted above, we had a preference for well-established findings that are known to replicate, though for sake of diversity this was not always possible. Table \@ref(tab:studies-table) provides an overview of the five studies we selected.

@@

All data and analysis code underlying this paper can be found in the Github repository: <https://github.com/jodeleeuw/219-2021-eyetracking-analysis>. The current paper is fully reproducible by rendering `manuscript.Rmd`.

@@

We used a fork of the `webgazer.js` library for webcam eye-tracking [@papoutsaki2016webgazer], implemented in `jsPsych`, a Javascript library for running behavioral experiments in a web browser [@deleeuwJsPsychJavaScriptLibrary2015].[^2] Our fork included changes to `webgazer.js` in order to improve data quality for experiments in which the precise timing of stimulus onsets is relevant. Specifically, we implemented a polling mode so that gaze predictions could be requested at a regular interval, which improved the sampling rate considerably in informal testing. This modification is similar to what Yang and Krajbich [-@yang2021webcam] reported improved the sampling rate in their study of webgazer. We also adjusted the mechanism for recording time stamps of each gaze prediction, so that the time stamp reported by webgazer is based on when the video frame is received and not when the computation of the gaze point is finished.

[^2]: The WebGazer.js patch can be found at <https://github.com/brownhci/WebGazer/commit/35301e56c192ef265bb270873a6526205f183711>.

@@

During the calibration, dots appeared on the screen one at a time in different locations, and the participants had to fixate them and click on each one. Once they clicked on a dot, it would disappear and a new one would appear in a different location on the screen. The locations of calibration dots were specific to each experiment (details below) and appeared in the areas of the screen where the visual stimuli would appear during the main task in order to ensure that eye movements were accurately recorded in the relevant regions of interest. After the calibration was completed, the validation began. Participants were asked to go through the same steps as the calibration, except that they only fixated the dots as they appeared in different locations on the screen. If accuracy on the validation was too low (fewer than 50% of looks landed within a 200 px radius of the validation points), participants were given an opportunity to re-start the calibration and validation steps. However, even participants with low calibration accuracy were allowed to complete the experiment, because we specifically wanted to study the consequences of low calibration accuracy.<!--If the second attempt also lead to low validation
accuracy, participants were informed that they could not participate in
the study.(AJ: I don't think this is true, as there are Ps included that have under 50% on the second round of calibration)-->

Upon finishing calibration, participants were reminded to keep their head still for the remainder of the study.

@@

These data were collected within the context of an undergraduate research methods course. Groups of students (co-authors) designed and programmed experiments in jsPsych, pre-registered their planned analyses, and collected data through Prolific under the supervision of the last author. The OSF repositories associated with these experiments are linked in the methods sections of each individual study. Note that in the current paper we expand on those pre-registered analyses (e.g., including analyses of the calibration quality).

@@

Participants then proceeded to the second encoding and recall phases as described above. After completing both encoding-recall blocks, participants were asked to answer a few survey questions (such as whether they wore glasses or encountered any distractions).

@@

### Survey results

```{r E2-analysis-survey, child='group-b/E2-analysis-survey.Rmd'}

@@

The third study was a partial replication attempt of the "looking group" condition of @mannsVisualPairedcomparisonTask2000 (we did not replicate their priming condition). This experiment used the visual paired-comparison, which involves presenting a previously-viewed image and novel image together and measuring the proportion of time spent looking at each image. The expected pattern of results is that participants will look more at novel objects. @mannsVisualPairedcomparisonTask2000 hypothesized that this pattern of behavior could be used to measure the strength of memories. If a viewer has a weak memory of the old image, then they may look at the old and new images roughly the same amount of time. They tested this in two ways. First, they showed participants a set of images, waited five minutes, and then paired those images with novel images. They found that participants spent more time (58.8% of total time) looking at the novel images. They then measured memory performance one day later and found that participants were more likely to recall images that they had spent less time looking at during the visual paired-comparison task the previous day.

@@

Thus, most of the key findings replicated. What should we make of the finding that failed to replicate? Notably, the proportion of looks to the novel object on Day 1 (54% or 55%, depending on analysis) was numerically smaller than in the original (59%), potentially decreasing the ability to detect correlations with eye-gaze. If so, the question is whether that is due to lower-quality eye-gaze tracking. This seems unlikely, because calibration quality did not appear to substantially affect this result (or any of the others). Alternative explanation include the well-documented decline effect [replications tend to find smaller effect sizes than the original, @schooler2011unpublished; @open2015estimating; @hartshorne2012tracking] and the common finding that subject accuracy is lower when not testing undergraduates at elite universities [@hartshorne2019meta; @germine2012web].

@@

The fourth study was a replication attempt of Experiment 1 in @ryskinVerbBiasesAre2017, which was closely modeled on @snedekerDevelopingConstraintsParsing2004a. These studies used the visual world paradigm to show that listeners use knowledge of the co-occurrence statistics of verbs and syntactic structures to resolve ambiguity. For example, in a sentence like "Feel the frog with the feather," the phrase "with the feather" could be describing the frog, or it could be describing the instrument that should be used to do the "feeling." When both options (a frog holding a feather and a feather by itself) are available in the visual display, listeners rely on the verb's "bias" (statistical co-occurrence either in norming or corpora) to rapidly choose an action while the sentence is unfolding. Use of the verb's bias should be reflected in a greater proportion of eye-gaze fixations to the animal (e.g., frog) for verbs that are biased toward modifier structures relative to instrument structures and, conversely, a greater proportion of eye-gaze fixations to the instrument (e.g., feather) for verbs that are biased toward instrument structures relative to modifier structures.

@@

During a trial, four pictures were displayed (target animal, target instrument, distractor animal, distractor instrument), one in each corner of the screen, and participants heard an audio prompt that contained instructions about the action they needed to act out (e.g., "Rub the butterfly with the crayon"; see Figure \@ref(fig:E4-example-trial))[^3]. Using their cursor, participants could act out the instructions by clicking on objects and moving them or motioning over the objects[^4]. After the action was completed, the participants were instructed to press the space bar which led to a screen that said "Click Here" in the middle in order to remove bias in the eye and mouse movements from the previous trial. The experiment only allowed the participants to move on to the next trial once the audio was completely done playing and the mouse had been moved over at least one object.

[^3]: In the original study, the pictures appeared one by one on the screen and their names were played as they appeared. We removed this introductory portion of the trial to save time

[^4]: As opposed to the original study we recorded mouse movement instead of clicking behavior since not all of the audio prompts required clicking. For example, the sentence "locate the camel with the straw" may not involve any clicking but rather only mousing over the camel.

@@

This plug-in (and potentially other webcam-based eye-tracking options) opens the door to including a broader, more diverse sample of participants in cognitive science research. In contrast to the typical in-lab eye-tracking sample, which consists primarily of young university students from WEIRD countries [@henrich2010weirdest; @linxen2021weird; @de2023psychology; @rad2018toward], webcam eye-tracking can reach a much more diverse population, as the only prerequisite is access to a computer with a webcam (a standard feature on most modern laptops and tablets). While webcam eyetracking cannot by itself eliminate all demographic biases, some of which are in any case baked in by history [@henrich2020weirdest], it can help to reduce them, at least for studies amenable to the paradigm.

@@

The findings above suggest a few lessons for researchers wishing to conduct eyetracking studies with a webcam, as well as highlighting a few important methodological questions that need to be addressed going forward.

@@

Note also that while ROIs the size of quadrants are feasible, good calibration is important. Based on the results above, researchers using such paradigms may want to exclude data from participants with less than 50% validation accuracy. While stricter thresholds may decrease noise, they come at a cost. In preliminary analysis, we found that a threshold of 75% somewhat increased effect size in Exp. 4, but at the cost of reducing the sample size from 35 to 19. However, it could be helpful to more systematically investigate the optimal threshold and whether this varies by size of ROI.

There are a number of other interventions that might increase precision and should be investigated. For instance, it is possible to monitor head distance in real time [for an example, see @jiang2021easyeyes]; doing so and providing real-time feedback to participants should diminish noise. It may also be possible to automatically detect challenges to calibration accuracy (such as poor lighting) and provide targeted feedback. Similarly, it may be profitable to systematically study the parameters of eyegaze validation, for instance the number of validation points and the maximum distance allowed between gaze and target (set to 200px in the present study). These and other options should be investigated in order to determine how much they might improve precision.

Second, researchers need to take care with timing accuracy. Running studies on modern computers requires synchronizing multiple clocks, something that does not happen automatically. Failure to synchronize can result in substantial inaccuracies [@slim2022moving]. As indicated by the current work, the current jsPsych implementation of WebGazer.js has timing synchronization sufficient for many studies. We urge researchers to avoid using the current release of WebGazer.js as is, and instead either use jsPsych, our patch to WebGazer.js (<https://github.com/brownhci/WebGazer/commit/35301e56c192ef265bb270873a6526205f183711>), or other software that has been specifically documented as addressing common issues in timing for web-based eye-tracking.

Third, it is true for any eyetracker that precise data depends on good calibration, and good calibration depends in part on lighting and background [see, for instance, @yuksel2023investigation]. We suspect that it is possible to give subjects automated feedback on how to improve their own calibration, which could result in higher-quality data and fewer subject exclusions based on poor calibration.

@@

@@

4.  **Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.** Results from an in-lab study with an eyetracker (Panel A; James et al. 2023) are contrasted with the current results (Panel B). The vertical line marks the mean noun onset time across trials and conditions.

>>>>

---
title             : "What paradigms can webcam eye-tracking be used for? Attempted replications of five cognitive science experiments"
shorttitle        : "Webcam eye-tracking paradigms"
author:
  - name: Ariel N. James
    affiliation: '1'
    role:
      - Conceptualization
      - Formal analysis
      - Visualization
      - Writing - original draft
      - Writing - review & editing
    email: ajames2@macalester.edu
    corresponding: yes
    address: 1600 Grand Ave, Saint Paul, MN 55105, USA

@@

    email: jkhartshorne@mghihp.edu

@@

affiliation:
  - id: '1'
    institution: Psychology Department, Macalester College
  - id: '2'
    institution: Department of Cognitive & Information Science, University of California,
      Merced
  - id: '3'
    institution: Department of Communication Sciences and Disorders, MGH Institute of Health Professions
  - id: '4'
    institution: Cognitive Science Department, Vassar College
abstract: |

  Web-based data collection allows researchers to recruit large and diverse samples with fewer resources than lab-based studies require. Recent innovations have expanded the set of methodolgies that are possible online, but ongoing work is needed to test the suitability of web-based tools for various research paradigms. Here, we focus on webcam-based eye-tracking; we tested whether the results of five different eye-tracking experiments in the cognitive psychology literature would replicate in a webcam-based format. Specifically, we carried out five experiments by integrating two javascript-based tools: jsPsych and a modified version of Webgazer.js. In order to represent a wide range of applications of eye-tracking to cognitive psychology, we chose two psycholinguistic experiments, two memory experiments, and a decision-making experiment. These studies also varied in the type of eye-tracking display, including screens split into halves (Exps. 3 and 5) or quadrants (Exps. 2 and 4), or composed scenes with regions of interest that varied in size (Exp. 1). Outcomes were mixed. The least successful replication attempt was Exp. 1; we did not obtain a condition effect in our remote sample (1a), nor in an in-lab follow-up (1b). However, the other four experiments were more successful, replicating a blank-screen effect (Exp. 2), a novelty preference (Exp. 3), a verb bias effect (Exp. 4), and a gaze-bias effect in decision-making (Exp. 5). These results suggest that webcam-based eye tracking can be used to detect a variety of cognitive phenomena, including those with sensitive time, although paradigms that require high spatial resolution (like Exp. 1) should be adapted to coarser quadrant or split-half displays. 
keywords          : "eye-tracking, online, webcam, jsPsych, cognitive science"
wordcount         : "13,115"
bibliography      : ["references.bib"]
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
editor_options: 
  markdown: 
    wrap: 72
---

@@

The use of eye-tracking to study cognition took off when Alfred Yarbus
used suction cups to affix a mirror system to the sclera of the eye in
order to monitor eye position during the perception of images
[@yarbus1967eye]. In one study, participants viewed a painting depicting
multiple people in a complex interaction inside of a 19th century
Russian home. Yarbus showed, among other things, that the scan paths and
locations of fixations were largely dependent on the instructions given
to participants (e.g., View the picture freely vs. Remember the position
of the people and objects in the room). In other words, the cognitive
processing that the individual is engaged in drives the visuo-motor
system. Since these findings, eye-tracking has become a central method
in cognitive science research [for reviews, see @hayhoe2005eye,
@richardsonEyeTrackingResearch2004, @rayner1998eye]. For example, gaze
location during natural scene perception is used to test theories of
visual attention [e.g., @henderson2017meaning], and eye-movements during
auditory language comprehension, using the "visual world paradigm,"
demonstrated the context-dependent and incremental nature of language
processing [e.g., @tanenhaus1995].

An important limitation of the eye-tracking methodology is that it has
typically required costly equipment (eye-trackers can range in price
from a few thousand dollars to tens of thousands of dollars), particular
laboratory conditions (a quiet room with consistent indoor lighting
conditions), and a substantial time investment (e.g., bringing
participants into a laboratory one at a time). This limits who can
conduct eye-tracking research -- not all researchers have the necessary
resources -- and who can participate in eye-tracking research. Most
eye-tracking study participants are from western, educated,
industrialized, rich, and democratic [WEIRD; @henrich2010weirdest]
convenience samples [but see @ryskin2023real], which diminishes the
generalizability of the findings and the scope of conclusions that can
be drawn about human cognition. Likewise, the sample sizes for in-lab
experiments are usually orders of magnitude smaller than what
statisticians recommend [@nosek2022replicability].

A robust solution to all these problems is online experiments,
particularly with volunteer citizen scientists as participants
[@li2024developmental; @hartshorne2019thousand;
@reinecke2015labinthewild; @gosling2010wired]. Historically, this option
has not been available for eye-tracking, since few potential subjects
have expensive eyetrackers at home. In principal, this could be
circumvented by using so-called "poor-man's" eye-tracking, in which
researchers videotape the subject's face and code eye position
frame-by-frame [@snedeker2003using]. Most computers now have
high-quality built-in cameras, so recording video is straightforward.
Unfortunately, coding images frame-by-frame is extremely time-intensive,
making large-sample studies unrealistic. However, in recent years, image
analysis has improved to the point where this work can be automated with
reasonable accuracy [@papoutsaki2016webgazer; @zheng2018rapid;
@burton2014comparison; @skovsgaard2011evaluation]. Nonetheless,
webcam-based eyetracking only started to be used regularly in research
with the advent of `Webgazer.js` [@papoutsaki2016webgazer], a
webcam-based Javascript plug-in that works in the browser and which can
be integrated with any Javascript web interface, including `jsPsych`
[@deleeuwJsPsychJavaScriptLibrary2015], `Gorilla` [@anwyl2020gorilla],
or `lab.js` [@henninger2021lab].

@@

While promising, there are some salient limitations. First, many of the
studies report effects that are smaller or later than what had been
previously observed in the lab [@slim2022moving; @degen2021seeing;
@van2023validation]. Importantly, accurate timing on a web browser is
not trivial [@passell2021cognitive; @de2016psychophysics], and subtle
programming choices can significantly affect the accuracy of
`WebGazer.js` timing [@yang2021webcam].[^1] Since most of the prior work
did not address these timing issues, it is not clear how many of the
reported lab/web differences would resolve.

@@

Second, prior work has focused on studies with relatively coarse-grained
regions of interest [but see @semmelmann2018online], dividing the screen
either in half or in quadrants. This is particularly salient with
[@prystauka2023online], which simplified
@altmannIncrementalInterpretationVerbs1999's design so that regions of
interest are quadrants rather than the finer-grained ROIs used in the
original. Certainly, webcam eyetracking will not be as spatially
fine-grained as an infrared eyetracker, but we do not yet have a good
sense of the limits.

@@

In order to broaden the validation of online eye-tracking methodology,
we set out to reproduce five previously published studies representing a
variety of questions, topics, and paradigms. The goal was to examine the
strengths and weaknesses of webcam eye-tracking for common paradigms in
cognitive science, across a broad range of research areas. Critically,
we used the implementation known to have the greatest temporal precision
to date: `jsPsych` and a modification of `Webgazer`.

@@

<!-- June 2022: shimojo: 964 citations, altmann: 1840, ryskin: 75, johansson 190, 127 -->

<!-- RR: switched ryskin to Snedeker & trueswell 2004 bcs my 75 looked sad -->

We chose five high-impact eye-tracking studies involving adult subjects
[for an comparison of remote WebGazer and in-lab anticipatory looking
effects with 18-27 month-old participants, see @steffan2024validation].
Our goal was to include experiments from a range of topic areas (e.g.,
memory, decision making, psycholinguistics) and paradigms (two halves of
the screen, visual world paradigm with four quadrants, visual world
paradigm with "naturalistic" scenes). As noted above, we had a
preference for well-established findings that are known to replicate,
though for sake of diversity this was not always possible. Table
\@ref(tab:studies-table) provides an overview of the five studies we
selected.

@@

@@

We used a fork of the `webgazer.js` library for webcam eye-tracking
[@papoutsaki2016webgazer], implemented in `jsPsych`, a Javascript
library for running behavioral experiments in a web browser
[@deleeuwJsPsychJavaScriptLibrary2015]. Our fork included changes to
`webgazer.js` in order to improve data quality for experiments in which
the precise timing of stimulus onsets is relevant. Specifically, we
implemented a polling mode so that gaze predictions could be requested
at a regular interval, which improved the sampling rate considerably in
informal testing. This modification is similar to what Yang and Krajbich
[-@yang2021webcam] reported improved the sampling rate in their study of
webgazer. We also adjusted the mechanism for recording time stamps of
each gaze prediction, so that the time stamp reported by webgazer is
based on when the video frame is received and not when the computation
of the gaze point is finished.

@@

During the calibration, dots appeared on the screen one at a time in
different locations, and the participants had to fixate them and click
on each one. Once they clicked on a dot, it would disappear and a new
one would appear in a different location on the screen. The locations of
calibration dots were specific to each experiment (details below) and
appeared in the areas of the screen where the visual stimuli would
appear during the main task in order to ensure that eye movements were
accurately recorded in the relevant regions of interest. After the
calibration was completed, the validation began. Participants were asked
to go through the same steps as the calibration, except that they only
fixated the dots as they appeared in different locations on the screen.
If accuracy on the validation was too low (fewer than 50% of looks
landed within a 200 px radius of the validation points), participants
were given an opportunity to re-start the calibration and validation
steps. <!--If the second attempt also lead to low validation
accuracy, participants were informed that they could not participate in
the study.(AJ: I don't think this is true, as there are Ps included that have under 50% on the second round of calibration)-->

@@

These data were collected within the context of an undergraduate
research methods course. Groups of students (co-authors) designed and
programmed experiments in jsPsych, pre-registered their planned
analyses, and collected data through Prolific under the supervision of
the last author. The OSF repositories associated with these experiments
are linked in the methods sections of each individual study. Note that
in the current paper we expand on those pre-registered analyses (e.g.,
including analyses of the calibration quality). All analysis code
underlying this paper can be found in the Github repository:
<https://github.com/jodeleeuw/219-2021-eyetracking-analysis>

@@

Participants then proceded to the second encoding and recall phases as
described above. After completing both encoding-recall blocks,
participants were asked to answer a few survey questions (such as
whether they wore glasses or encountered any distractions).

@@

@@

The third study was a partial replication attempt of the "looking group"
condition of @mannsVisualPairedcomparisonTask2000 (we did not replicate
their priming condition). This experiment used the visual
paired-comparison, which involves presenting a previously-viewed image
and novel image together and measuring the proportion of time spent
looking at each image. The expected pattern of results is that
participants will look more at novel objects. They
@mannsVisualPairedcomparisonTask2000 hypothesized that this pattern of
behavior could be used to measure the strength of memories. If a viewer
has a weak memory of the old image, then they may look at the old and
new images roughly the same amount of time. They tested this in two
ways. First, they showed participants a set of images, waited five
minutes, and then paired those images with novel images. They found that
participants spent more time (58.8% of total time) looking at the novel
images. They then measured memory performance one day later and found
that participants were more likely to recall images that they had spent
less time looking at during the visual paired-comparison task the
previous day.

@@

Thus, most of the key findings replicated. What should we make of the
finding that failed to replicate? Notably, the proportion of looks to
the novel object on Day 1 (54% or 55%, depending on analysis) was
numerically smaller than in the original (59%), potentially decreasing
the ability to detect correlations with eye-gaze. If so, the question is
whether that is due to lower-quality eye-gaze tracking. This seems
unlikely, because calibration quality did not appear to substantially
affect this result (or any of the others). Alternative explanation
include the well-documented decline effect (replications tend to find
smaller effect sizes than the original) and the common finding that
subject accuracy is lower when not testing undergraduates at elite
universities.

@@

The fourth study was a replication attempt of Experiment 1 in
@ryskinVerbBiasesAre2017, which was closely modeled on
@snedekerDevelopingConstraintsParsing2004a. These studies used the
visual world paradigm to show that listeners use knowledge of the
co-occurrence statistics of verbs and syntactic structures to resolve
ambiguity. For example, in a sentence like "Feel the frog with the
feather," the phrase "with the feather" could be describing the frog, or
it could be describing the instrument that should be used to do the
"feeling." When both options (a frog holding a feather and a feather by
itself) are available in the visual display, listeners rely on the
verb's "bias" (statistical co-occurrence either in norming or corpora)
to rapidly choose an action while the sentence is unfolding. .

@@

During a trial, four pictures were displayed (target animal, target
instrument, distractor animal, distractor instrument), one in each
corner of the screen, and participants heard an audio prompt that
contained instructions about the action they needed to act out (e.g.,
"Rub the butterfly with the crayon"; see
Figure \@ref(fig:E4-example-trial))[^2]. Using their cursor,
participants could act out the instructions by clicking on objects and
moving them or motioning over the objects[^3]. After the action was
completed, the participants were instructed to press the space bar which
led to a screen that said "Click Here" in the middle in order to remove
bias in the eye and mouse movements from the previous trial. The
experiment only allowed the participants to move on to the next trial
once the audio was completely done playing and the mouse had been moved
over at least one object.

[^2]: In the original study, the pictures appeared one by one on the
    screen and their names were played as they appeared. We removed this
    introductory portion of the trial to save time

[^3]: As opposed to the original study we recorded mouse movement
    instead of clicking behavior since not all of the audio prompts
    required clicking. For example, the sentence "locate the camel with
    the straw" may not involve any clicking but rather only mousing over
    the camel.

@@

@@

The findings above suggest a few lessons for researchers wishing to
conduct eyetracking studies with a Webcam, as well as highlighting a few
important methodological questions that need to be addressed going
forward.

@@

Note also that while ROIs the size of quadrants are feasible, good
calibration is important. Based on the results above, researchers using
such paradigms may want to exclude data from participants with less than
75% validation accuracy, whereas studies using two halves of the display
as ROIs may not need to be so conservative.

Second, researchers need to take care with timing accuracy. Running
studies on modern computers requires synchronizing multiple clocks,
something that does not happen automatically. Failure to synchronize can
result in substantial inaccuracies [@slim2022moving]. As indicated by
the current work, the current jsPsych implementation of WebGazer.js has
reasonably good timing synchronization. We recommend that future
researchers use jsPsych or another package with similar documented
precision.

Third, it is true for any eyetracker that precise data depends on good
callibration, and good callibration depends in part on lighting and
background. We suspect that it is possible to give subjects automated
feedback on how to improve their own calibration, which could result in
higher-quality data and fewer subject exclusions based on poor
calibration.

@@

# Ethics statement

The remote experiments (1a, 2-5) were conducted with approval by the
Vassar College Institutional Review Board. The laboratory experiment
(1b) was conducted with approval by the Boston College Institutional
Review Board.

@@

4.  **Cumulative probability of fixating distractor and target objects
    across conditions over time, with 0 ms aligned to the verb onset
    time.** Results from an in-lab study with an eyetracker (Panel A;
    @james2023language) are contrasted with the current results (Panel
    B). The vertical line marks the mean noun onset time across trials
    and conditions.
